Outbreaks in Toronto Healthcare Institutions After COVID-19

### 2024-09-24 paper/paper.qmd
Update paper.qmd

---
title: "Outbreaks in Toronto Healthcare Institutions After COVID-19"
subtitle: "Analysis of the Causative Agents and Trend of Fluctuations"
author: 
  - Yunkyung Ko
thanks: "Code and data are available at: https://github.com/koyunkyung/paper1_draft.git."
date: today
date-format: long
abstract: "In Canada, outbreak incidence has been slowly increasing from June 2024 up to the beginning of the accumulating data period on August 10, 2024. (ADD CITATION https://health-infobase.canada.ca/covid-19/) Using the 'Outbreaks in Toronto Healthcare Institutions' dataset, we show how the trends of outbreak occurrence has been over the 5 years after COVID-19. (specify headline result). (implications)."
format: pdf
number-sections: true
bibliography: references.bib
---

>>>>

---
title: "Outbreaks in Toronto Healthcare Institutions After COVID-19"
subtitle: "Analysis of the Frequency Trends and the Causative Agent"
author: 
  - Yunkyung Ko
thanks: "Code and data are available at: https://github.com/koyunkyung/paper1_draft.git."
date: today
date-format: long
abstract: "In Canada, outbreak incidence has been slowly increasing from June 2024 up to the beginning of the accumulating data period on August 10, 2024. (ADD CITATION https://health-infobase.canada.ca/covid-19/) Using the 'Outbreaks in Toronto Healthcare Institutions' dataset, we show how the trends of outbreak occurrence has been over the 5 years after COVID-19. (specify headline result). (implications)."
format: pdf
number-sections: true
bibliography: references.bib
---
